MG7: Configurable and scalable 16S data analysis

### 2016-08-18 docs/mg7-paper/out/paper.tex

The second step is to search for similar 16S sequences in our 16S-DB7
database. The taxonomic assignment for each read is based on BLASTN of
each read against the 16S database.Assignment based on direct similarity
of each read one by one compared against a sufficiently wide database is
considered in different reviews of metagenomics analysis methodologies
\citep{segata2013computational} \citep{morgan2012chapter} as a very
exhaustive method for assignment. Some methods of assignment compare the
sequences only against the 16S genes from available complete bacterial
genomes or avoid computational cost clustering or binning the sequences
first, and then doing the assignments only for the representative
sequence of each cluster. MG7 carries out an exhaustive comparison of
all the reads under analysis and it does not applies any binning
strategy. Every read is specifically compared with all the sequences of
the 16S database.

@@

\paragraph{LCA Assignment}\label{lca-assignment}

@@

\paragraph{Best BLAST hit taxonomic
assignment}\label{best-blast-hit-taxonomic-assignment}

>>>>

The second step is to search for similar 16S sequences in our 16S-DB7
database. The taxonomic assignment for each read is based on BLASTN of
each read against the 16S database. Assignment based on direct
similarity of each read one by one compared against a sufficiently wide
database is considered in different reviews of metagenomics analysis
methodologies \citep{segata2013computational} \citep{morgan2012chapter}
as a very exhaustive method for assignment. Some methods of assignment
compare the sequences only against the 16S genes from available complete
bacterial genomes or avoid computational cost clustering or binning the
sequences first, and then doing the assignments only for the
representative sequence of each cluster. MG7 carries out an exhaustive
comparison of all the reads under analysis and it does not apply any
binning strategy. Every read is specifically compared with all the
sequences of the 16S database.

@@

\paragraph{LCA assignment}\label{lca-assignment}

@@

\paragraph{Best BLAST hit assignment}\label{best-blast-hit-assignment}
